Manuscript

### 2018-10-30 manuscript.Rmd
updated pval vs g2p evidence summary

```{r}
library(bsselectR)
library(data.table)
library(ggExtra)
library(ggpubr)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

```{r fig.height=4, fig.width=12}
g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))

g2p_druggene_all_mad_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.2), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  geom_rug(size = 1) +
  theme(legend.position = "top")
g2p_druggene_all_mad_summ_plot

g2p_druggene_all_p_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "top")
g2p_druggene_all_p_summ_plot

# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

>>>>

```{r}
library(bsselectR)
install.packages("cowplot")
library(data.table)
library(ggpubr)
library(ggsignif)
library(grid)
library(gridExtra)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

```{r, eval=FALSE, include=FALSE}
plot_mad_ccle_a <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.2), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "top")

plot_p_a <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "top")
```

```{r}
g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
```

```{r fig.height=7, fig.width=12}
## MAD
plot_mad_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_mad_point <- ggplot_gtable(ggplot_build(plot_mad_point))
plot_mad_box <- ggplot_gtable(ggplot_build(plot_mad_box))
mad_maxWidth <-  grid::unit.pmax(plot_mad_point$widths, plot_mad_box$widths)
plot_mad_point$widths <- as.list(mad_maxWidth)
plot_mad_box$widths <- as.list(mad_maxWidth)

g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
                   plot_mad_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_mad_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")

## P-value
plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
plot_p_point$widths <- as.list(p_maxWidth)
plot_p_box$widths <- as.list(p_maxWidth)

g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_druggene_all_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
```
